Contextual Combinatorial Cascading Bandits

### 2016-01-07 contextual combinatorial cascading bandits.tex

The cascade model is popular to describe user behavior in recommendation systems. When recommended with a list of items, such as web pages or advertisements, the user checks from the first item to the last and selects the first attractive item. The items before the selected one are not attractive and the items after the selected one are unobserved. Also in networking routing problem, if we want to check whether a path is unblocked, we can just stop checking if an blocked edge appears. The cascade model is useful to describe such kind of partial-observation problem. In both recommendation and network routing problem, historical information will usually help to provide more effective choices.

>>>>

The cascade model is popular to describe user behaviors in recommendation systems. When recommended with a list of items, such as web pages or advertisements, the user checks from the first item to the last and selects the first attractive item. The items before the selected one are not attractive and the items after the selected one are unobserved. Also in networking routing problem, if we want to check a path from source to end to confirm whether it is blocked, we can just stop checking when meeting a blocked edge. The cascade model is useful to describe such kind of partial-observation problem.

Now personalized recommendation is a basic feature of websites to improve user satisfaction by providing attractive content to meet specific user's need. Personalization includes storing user features and historical information, managing content set, analysis of user behaviors and providing suitable content to the user. Usually, both users and content are represented by feature sets. User features may contain basic attributes, like age, gender and nationality, and historical behaviors. Content features may contain categories and descriptive information. Because the views of different users on the same content can vary significantly, exploration and exploitation have to be exercised at an individual level and be able to cross different contents.
